### 2022-07-18 dev/notebooks/synthetic.qmd
some progress on experiment set up

```{julia}
Random.seed!(1234)
using MLJ
N = 1000
X, ys = make_blobs(N, 2; centers=2, as_table=false, center_box=(-2 => 2), cluster_std=0.1)
ys .= ys.==2
X = X'
xs = Flux.unstack(X,2)
data = zip(xs,ys)
counterfactual_data = CounterfactualData(X,ys')
```

@@

```{julia}
μ = 0.10
Random.seed!(123)
candidates = findall(ys.==0)
chosen = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
using CounterfactualExplanations.Counterfactuals: counterfactual, counterfactual_label
for i in chosen
    x = X[:,i]
    outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen,γ=γ)
    X′[:,i] = counterfactual(outcome)
    y′[i] = counterfactual_label(outcome)
end
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)")
```

@@

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    Random.seed!(123)
    candidates = findall(y′.==0)
    chosen = rand(candidates, Int(round(μ*length(candidates))))
    mod = Models.train(mod, counterfactual_data′; n_epochs=n_epochs)
    for i in chosen
        x = X′[:,i]
        outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen; γ=γ)
        X′[:,i] = counterfactual(outcome)
        y′[i] = counterfactual_label(outcome)
    end
    i += 1
end
plt_single_repeat = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)")
```

@@

```{julia}
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(μ, γ)
n_rounds = 10
n_folds = 5
target = 1.0
T = 1000
```

@@

```{julia}
function plot_state(path, t; γ=0.75, μ = 0.05, k = 1, length_out=500, size=(150,150), title="")
    chosen = map(p -> p.γ == γ && p.μ == μ && p.t==t && p.k==k, path)
    path = path[chosen][1]
    X = path.X̲'
    y = vec(path.y̲')
    plt = plot_contour(X,y,path.𝑴,length_out=length_out,colorbar=cb,title=title)
    plt = plot(plt, axis=nothing, size=size, legend=false)
end
plot_state(paths[2], 1)
```

>>>>

```{julia}
using MLJ
N = 1000
X, ys = make_blobs(N, 2; centers=2, as_table=false, center_box=(-2 => 2), cluster_std=0.1)
ys .= ys.==2
X = X'
xs = Flux.unstack(X,2)
data = zip(xs,ys)
counterfactual_data = CounterfactualData(X,ys')
```

@@

```{julia}
μ = 0.10
candidates = findall(ys.==0)
chosen = rand(candidates, Int(round(μ*length(candidates))))
X′ = copy(X)
y′ = copy(ys)
using CounterfactualExplanations.Counterfactuals: counterfactual, counterfactual_label
for i in chosen
    x = X[:,i]
    outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen,γ=γ)
    X′[:,i] = counterfactual(outcome)
    y′[i] = first(counterfactual_label(outcome))
end
counterfactual_data′ = CounterfactualData(X′,y′')
plt_single = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(b)")
```

@@

```{julia}
i = 2
while i <= 10
    counterfactual_data′ = CounterfactualData(X′,y′')
    candidates = findall(y′.==0)
    chosen = rand(candidates, Int(round(μ*length(candidates))))
    H₀ = mod.model.H # use posterior as new prior
    mod = Models.train(mod, counterfactual_data′; n_epochs=n_epochs, H₀=H₀)
    for i in chosen
        x = X′[:,i]
        outcome = generate_counterfactual(x, 1, counterfactual_data, mod, gen; γ=γ)
        X′[:,i] = counterfactual(outcome)
        y′[i] = first(counterfactual_label(outcome))
    end
    i += 1
end
plt_single_repeat = plot(mod,counterfactual_data′;zoom=0,colorbar=false,title="(d)")
```

@@

```{julia}
using AlgorithmicRecourseDynamics.Experiments
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(models, generators, μ, γ)
n_rounds = 5
n_folds = 1
target = 1.0
T = 1000
```

@@

```{julia}
function plot_state(path, t; γ=0.75, μ = 0.05, k = 1, length_out=500, size=(150,150), title="")
    chosen = map(p -> p.γ == γ && p.μ == μ && p.t==t && p.k==k, path)
    path = path[chosen][1]
    X = path.X̲'
    y = vec(path.y̲')
    plt = plot_contour(X,y,path.M,length_out=length_out,colorbar=cb,title=title)
    plt = plot(plt, axis=nothing, size=size, legend=false)
end
plot_state(paths[2], 1)
```

### 2022-07-18 dev/resources/misc/boston_housing.qmd
some progress on experiment set up

```{julia}
using BSON: @load
@load joinpath(output_folder, "nn.bson") nn
𝑴ₙₙ = Models.FittedNeuralNet(nn, opt, loss);
```

@@

```{julia}
ensemble = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
𝑴 = Models.FittedEnsemble(ensemble, opt, loss_type);
```

@@

```{julia}
# Experiment:
experiment = Experiments.Experiment(X,y,𝑴ₙₙ,target,grid_,n_rounds);
```

@@

```{julia}
# Experiment:
experiment = Experiments.Experiment(X,y,𝑴,target,grid_,n_rounds);
```

>>>>

```{julia}
using BSON: @load
@load joinpath(output_folder, "nn.bson") nn
Mₙₙ = Models.FittedNeuralNet(nn, opt, loss);
```

@@

```{julia}
ensemble = Models.load_ensemble(root=joinpath(output_folder, "ensemble"))
M = Models.FittedEnsemble(ensemble, opt, loss_type);
```

@@

```{julia}
# Experiment:
experiment = Experiments.Experiment(X,y,Mₙₙ,target,grid_,n_rounds);
```

@@

```{julia}
# Experiment:
experiment = Experiments.Experiment(X,y,M,target,grid_,n_rounds);
```

### 2022-07-18 dev/resources/misc/synthetic_bayesian_ar.qmd
some progress on experiment set up

```{julia}
using CounterfactualExplanations.Models: BayesianLogisticModel
𝑴 = BayesianLogisticModel(reshape(model.μ,1,length(model.μ)), model.Σ); # repare for usage with CounterfactualExplanations.jl
x̅ = [50.0, 60.0]; # factual
using Random
Random.seed!(1234)
y̅ = round(CounterfactualExplanations.Models.probs(𝑴, x̅)[1])
target = ifelse(y̅==1.0,0.0,1.0) # opposite label as target
γ = ifelse(target==1.0,0.9,0.1); # desired threshold based on target
```

@@

```{julia}
recourse_generic = generate_recourse(generic, x̅, 𝑴, target, γ) # generate recourse
recourse_greedy = generate_recourse(greedy, x̅, 𝑴, target, γ);
```

>>>>

```{julia}
using CounterfactualExplanations.Models: BayesianLogisticModel
M = BayesianLogisticModel(reshape(model.μ,1,length(model.μ)), model.Σ); # repare for usage with CounterfactualExplanations.jl
x̅ = [50.0, 60.0]; # factual
using Random
Random.seed!(1234)
y̅ = round(CounterfactualExplanations.Models.probs(M, x̅)[1])
target = ifelse(y̅==1.0,0.0,1.0) # opposite label as target
γ = ifelse(target==1.0,0.9,0.1); # desired threshold based on target
```

@@

```{julia}
recourse_generic = generate_recourse(generic, x̅, M, target, γ) # generate recourse
recourse_greedy = generate_recourse(greedy, x̅, M, target, γ);
```
